---
title: "Orbit fMRI Behavioral Data"
output: 
  html_notebook: 
    code_folding: hide
    theme: spacelab
    toc: true
    toc_float: true
    fontsize: 6pt
---
<style type="text/css">
body{ /* Normal  */
      font-size: 14px}
td {  /* Table  */
  font-size: 12px}
h1.title {
  font-size: 30px}
h1 { /* Header 1 */
  font-size: 24px}
h2 { /* Header 2 */
    font-size: 20px}
code.r{ /* Code block */
    font-size: 12px}
</style>


This report contains all analyses of Orbit fMRI *behavioral* data.  

N = 28/34 -->  
2 subjects did not complete the experiment due to anxiety/movement in the scanner and 4 subjects were excluded due to chance level behavior, defined as a mean absolute error of > 75 degrees (where chance = 90) in any condition (color, scene).  

Mixture model functions are from: https://github.com/eddjberry/precision-mixture-model  


```{r, include=FALSE}

#### load in all necessary packages:
library('ggplot2')
library('tidyr')
library('dplyr')
library('ez')
library('lsr')
library('psych')
library('knitr')
library('pander')

taskVer <- 'fMRI-behavior'
### define computer path
#myComp <- '/Users/memolab/Google Drive/'
myComp <- '/Users/rosecooper/Documents/'

### define all functions:
source(paste(myComp,'Work/Methods/myFunctions/General/multiplot.R',sep = "")) 
source(paste(myComp,'Work/Methods/myFunctions/BaysPrecision/mixture_model_functions.R',sep = "")) 

se <- function(x) sqrt(var(x)/length(x))  #function to calculate SE
ci <- function(x) (sqrt(var(x)/length(x)))*1.96  #function to calculate 95% confidence interval
zscore <- function(x,data) (x - mean(data))/sd(data)  #allows values to be z scored relative to itself (x = data) or a different variable (x != data)


### load in all behavioral data:
myFile <- paste(myComp,'Work/Boston/ORBIT/analysis/',taskVer,'/AllData_',taskVer,'.csv',sep = "")
allData <- data.frame(read.csv(myFile, header = TRUE))

# add column for emotion confidence level:
allData$EmotionMemory[allData$EmotionCorrect == 1 & allData$EmotionConfidence == 1] <- 1
allData$EmotionMemory[allData$EmotionCorrect == 1 & allData$EmotionConfidence == 0] <- 0.5
allData$EmotionMemory[allData$EmotionCorrect == 0] <- 0

subjects <- unique(allData$SubID)
NSubjs = length(subjects)

```

# Feature Errors
Response - Study angle across all subjects plotted as density histograms per feature.  
Overlayed is the best fitting mixture model pdf (vonMises + uniform)  
```{r, fig.width=6,fig.height=2.5}

### All Color and Scene
### Fit mixture model to aggregate data (needs to be in radians):
Color <- JV10_fit(wrap(allData$ColResp/180*pi), wrap(allData$ColStudy/180*pi))
print(paste0("Color : % Correct = ", round(Color$B$Pt, digits = 4)))
print(paste0("      : Precision = ", round(Color$B$K, digits = 4)))

Scene <- JV10_fit(wrap(allData$SceneResp/180*pi), wrap(allData$SceStudy/180*pi))
print(paste0("Scene : % Correct = ", round(Scene$B$Pt, digits = 4)))
print(paste0("      : Precision = ", round(Scene$B$K, digits = 4)))

### now get best fitting PDFs:
range = seq(from = -pi, to = pi, by = pi/180)
# 1. Get von Mises pdf based on aggregate precision
yCol = vonmisespdf(range,0,Color$B$K)
ySce = vonmisespdf(range,0,Scene$B$K)
# scale so area of distribution = proportion correct
yCol = yCol * (Color$B$Pt/(sum(yCol)))
ySce = ySce * (Scene$B$Pt/(sum(ySce)))
# 2. add guess rate (uniform component)
yCol = data.frame(yCol + (Color$B$Pu/length(range)))
ySce = data.frame(ySce + (Scene$B$Pu/length(range)))

colnames(yCol)<- c("prob")
yCol$error <- seq(from = -180, to = 180, by = 1)
colnames(ySce)<- c("prob")
ySce$error <- seq(from = -180, to = 180, by = 1)


# Threshold for memory 'success' (at least 50% chance that error fits von Mises), rounded to nearest multiple of 3 (my unique angles):
colT <-  max(abs(yCol$error[yCol$prob > (Color$B$Pu/length(range)*2)]))
colT <- 3*round(colT/3) 
sceT <-  max(abs(ySce$error[ySce$prob > (Scene$B$Pu/length(range))*2]))
sceT <- 3*round(sceT/3) 
print(paste("Threshold for color memory success at 50% <= ", colT, " degrees", sep = ""))
print(paste("Threshold for scene memory success at 50% <= ", sceT, " degrees", sep = ""))

# add on Color and Scene accuracy columns to alldata based on model threshold:
allData$ColorCorrect[allData$ColAbsError <= colT] <- 1
allData$ColorCorrect[allData$ColAbsError > colT] <- 0
allData$SceneCorrect[allData$SceAbsError <= sceT] <- 1
allData$SceneCorrect[allData$SceAbsError > sceT] <- 0

# plot data with line at height of uniform distribution:
p1 <- ggplot(allData, aes(x = ColError)) +
    geom_histogram(bins = 61, color = 'white', fill = 'gray60', aes(y=..density..), 
                   position=position_dodge(1)) + 
    geom_line(data = yCol, aes(x = error, y = prob), color = 'coral2', size=1.5) +
    xlab("Error") + ylab("p(Error)") +
    scale_y_continuous(limits = c(0,0.020), expand = c(0,0), breaks = seq(0,0.020,by = 0.005)) + 
    scale_x_continuous(expand = c(0,0), breaks = seq(-180,180,by = 60)) + 
    ggtitle("Color Errors") +
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 20), axis.title = element_text(size = 24),
          panel.background = element_blank(),
          legend.position="none", text = element_text(family="Helvetica"))  

ggsave('Color_Errors.jpg', plot = p1, dpi = 300, width = 6.5, height = 5)

p2 <- ggplot(allData, aes(x = SceError)) +
    geom_histogram(bins = 61, color = 'white', fill = 'gray60', aes(y=..density..),
                   position=position_dodge(1)) + 
    geom_line(data = ySce, aes(x = error, y = prob), color = 'dodgerblue2', size=1.5) +
    xlab("Error") + ylab("p(Error)") +
    scale_y_continuous(limits = c(0,0.032), expand = c(0,0), breaks = seq(0,0.032,by = 0.008)) + 
    scale_x_continuous(expand = c(0,0), breaks = seq(-180,180,by = 60)) + 
    ggtitle("Scene errors") +
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 20), axis.title = element_text(size = 24),
          panel.background = element_blank(),
          legend.position="none", text = element_text(family="Helvetica"))     

ggsave('Scene_Errors.jpg', plot = p2, dpi = 300, width = 6.5, height = 5)

multiplot(p1,p2, cols = 2)

```

# Subject Mixture Model by Color/Scene Feature
```{r, fig.width=5,fig.height=3}

### Compute mixture model estimates by subject and feature
mixture <- data.frame(matrix(0, nrow = NSubjs*2, ncol = 4))
names(mixture) <- c("SubID","Feature","pT","k")

row <- 0
for (idx in 1:length(subjects)) {
    myData <- subset(allData, SubID == as.integer(subjects[idx]))

    row = row + 1
    mixture$SubID[row]   = myData$SubID[1]
    mixture$Feature[row] = 'Color'
    curModel <- JV10_fit(wrap(myData$ColResp/180*pi), wrap(myData$ColStudy/180*pi))
    mixture$pT[row] <- curModel$B$Pt
    mixture$k[row]  <- curModel$B$K

    row = row + 1
    mixture$SubID[row]   = myData$SubID[1]
    mixture$Feature[row] = 'Scene'
    curModel <- JV10_fit(wrap(myData$SceneResp/180*pi), wrap(myData$SceStudy/180*pi))
    mixture$pT[row] <- curModel$B$Pt
    mixture$k[row]  <- curModel$B$K
  }#end of loop through subjects    

mixture$SubID <- as.factor(mixture$SubID)
mixture$Feature <- as.factor(mixture$Feature)
mixture <- mixture %>% group_by(Feature) #group data by these factors


# Memory Success (proportion correct)
p1 <- ggplot(mixture, aes(x=Feature, y=pT, color=Feature, fill=Feature)) +
    stat_summary(fun.y = mean, geom="bar", alpha = 0.4, position = position_dodge(1)) +
    scale_fill_manual(values = c('coral2','dodgerblue2')) + 
    scale_color_manual(values = c('coral2','dodgerblue2')) +
    geom_dotplot(binaxis='y', stackdir='center', alpha = 0.8, position = position_dodge(1)) +
    stat_summary(fun.data = mean_se, geom = "errorbar", fun.args = list(mult = 1.96),
                 width = 0.4, color = "black", size = 0.6, position = position_dodge(1)) +
    ggtitle("Memory Success") +  scale_y_continuous(expand = c(0,0), limits=c(0,1)) + 
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 22), axis.title = element_text(size = 22),
          panel.background = element_blank(),
          legend.position="none", text = element_text(family="Helvetica"))

# Precision summary
p2 <- ggplot(mixture, aes(x=Feature, y=k, color=Feature, fill=Feature)) +
    stat_summary(fun.y = mean, geom="bar", alpha = 0.4, position = position_dodge(1)) +
    scale_fill_manual(values = c('coral2','dodgerblue2')) +
    scale_color_manual(values = c('coral2','dodgerblue2')) +
    geom_dotplot(binaxis='y', stackdir='center', alpha = 0.8, position = position_dodge(1)) +
    stat_summary(fun.data = mean_se, geom = "errorbar", fun.args = list(mult = 1.96),
                 width = 0.4, color = "black", size = 0.6, position = position_dodge(1)) +
    ggtitle("Memory Precision") + scale_y_continuous(expand = c(0,0), limits=c(0,84)) + 
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 22), axis.title = element_text(size = 22),
          panel.background = element_blank(),
          legend.position="none", text = element_text(family="Helvetica"))

multiplot(p1,p2, cols = 2)

pander(t.test(pT ~ Feature, data=mixture, paired = TRUE))
pander(t.test(k ~ Feature, data=mixture, paired = TRUE))

# for saving data in csv:
pT <- subset(mixture, select = -c(k)) %>%
       spread(key = Feature, value = pT)
colnames(pT) <- c('SubID','ColorpT','ScenepT')
k <- subset(mixture, select = -c(pT)) %>%
       spread(key = Feature, value = k)
colnames(k) <- c('SubID','Colork','Scenek')

group_data <- merge.data.frame(pT,k,by='SubID') %>%
               sortFrame(SubID)

```

## Emotion Memory
Proportion correct and proportion of high confidence correct emotion responses  
```{r, fig.width=3,fig.height=1.8}

### Emotion accuracy (proportion correct)
emotion <- allData %>% 
                group_by(SubID) %>% 
                 summarise(EmotionSuccess = mean(EmotionCorrect)) 
group_data <- merge.data.frame(group_data, emotion, by = 'SubID')

summary <- emotion %>%
             summarise(EmotionCorrect = mean(EmotionSuccess), SE = se(EmotionSuccess))
print(kable(summary))

### Proportion of corect repsonses that were high confidence
correctData <- subset(allData, EmotionCorrect == 1)
confidence <- correctData %>% 
                group_by(SubID) %>% 
                 summarise(EmotionConfidence = mean(EmotionConfidence))
group_data <- merge.data.frame(group_data, confidence, by = 'SubID')

summary <- confidence %>%
             summarise(EmotionConfidence = mean(EmotionConfidence), SE = se(EmotionConfidence))
print(kable(summary))

```

# Memory Dependency
## Retrieval Success
Uses the dependent vs independent approach from Horner & Burgess (2013/2014) to estimate dependency of correct retrieval for each feature pair  
```{r, fig.width=4,fig.height=3}

dependency <- data.frame(matrix(0, nrow = NSubjs*3, ncol = 3))
names(dependency) <- c("SubID","Pair","Difference")

row <- 0
for (idx in 1:length(subjects)) {
    myData <- subset(allData, SubID == as.integer(subjects[idx]))
   
    for (pair in 1:3) {
      if (pair == 1) {
        name = 'Emotion-Color'
        curAcc <- cbind(myData$EmotionCorrect,myData$ColorCorrect)
      } else if (pair == 2) {
        name = 'Emotion-Scene'
        curAcc <- cbind(myData$EmotionCorrect,myData$SceneCorrect)
      } else if (pair == 3) {
        name = 'Color-Scene'
        curAcc <- cbind(myData$ColorCorrect,myData$SceneCorrect)
      }
      
      row = row + 1
      dependency$SubID[row]   = myData$SubID[1]
      dependency$Pair[row]    = name
      data  = length(which(!rowSums(curAcc) ==1))/nrow(curAcc)
      sumAcc <- colMeans(curAcc)
      independent = ((sumAcc[1]*sumAcc[2])+((1-sumAcc[1])*(1-sumAcc[2])))
      dependency$Difference[row] = data - independent
     }
  }#end of loop through subjects    

dependency$Pair <- as.factor(dependency$Pair)

# data vs independent model by feature
success <- dependency %>% 
              group_by(SubID, Pair)

p1 <- ggplot(success, aes(x = Pair, y=Difference, fill=Pair)) +
    stat_summary(fun.y = mean, geom="bar", alpha = 0.5) +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1, alpha = 0.8) +
    stat_summary(fun.data = mean_se, geom = "errorbar", fun.args = list(mult = 1.96),
                 width = 0.4, color = "black", size = 0.6) +
    scale_fill_manual(values = c('#66bd63','coral2','dodgerblue2')) + 
    ylab("Data - Independent") + scale_y_continuous(limits = c(-0.12,0.24),
                                                    expand = c(0,0),
                                                    breaks = seq(-0.12,0.24,by = 0.06)) +
    ggtitle("Retrieval Success Dependence") + geom_hline(yintercept = 0) +
    scale_x_discrete(labels=c("Color\nScene","Color\nEmotion","Scene\nEmotion")) +
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 20), axis.title = element_text(size = 24),
          panel.background = element_blank(),
          legend.position="none", text = element_text(family="Helvetica"))   

plot(p1)
ggsave('Correct_Dependency.jpg', plot = p1, dpi = 300, width = 6, height = 5)

#t-tests, greater than 0?
pander(t.test(success$Difference[success$Pair == 'Color-Scene'], mu=0))
pander(t.test(success$Difference[success$Pair == 'Emotion-Color'], mu=0))
pander(t.test(success$Difference[success$Pair == 'Emotion-Scene'], mu=0))

# for saving data in csv:
success <- success %>%
               spread(key = Pair, value = Difference)
group_data <- merge.data.frame(group_data,success,by='SubID') %>%
                sortFrame(SubID)

```

### Retrieval Precision
Computes the correlations between color and scene success (1 0) and precision (reversed 'correct' error).  
```{r, fig.width=4,fig.height=3}

dependency <- data.frame(matrix(0, nrow = NSubjs*3, ncol = 3))
names(dependency) <- c("SubID","Pair","Dependency")

row <- 0
for (idx in 1:length(subjects)) {

  for (pair in 1:3) {
    row = row + 1
    if (pair == 1) {
       myData <- subset(allData, SubID == subjects[idx] & ColorCorrect == 1 & SceneCorrect == 1)
       name = 'ColorP-SceneP'
       dependency$Dependency[row]  = fisherz(cor(180 - myData$ColAbsError,180 - myData$SceAbsError))
    } else if (pair == 2) {
       myData <- subset(allData, SubID == subjects[idx] & SceneCorrect == 1)
       name = 'ColorS-SceneP'
       dependency$Dependency[row]  = fisherz(cor(myData$ColorCorrect,180 - myData$SceAbsError))
    } else if (pair == 3) {
       myData <- subset(allData, SubID == subjects[idx] & ColorCorrect == 1)
       name = 'SceneS-ColorP'
       dependency$Dependency[row]  = fisherz(cor(myData$SceneCorrect,180 - myData$ColAbsError))
    }
    dependency$SubID[row] = myData$SubID[1]
    dependency$Pair[row]  = name
   }
  }#end of loop through subjects    

dependency$Pair <- as.factor(dependency$Pair)

# correlations by pair
precision <- dependency %>% 
              group_by(SubID, Pair)

p1 <- ggplot(precision, aes(x = Pair, y=Dependency, fill=Pair)) +
    stat_summary(fun.y = mean, geom="bar", alpha = 0.5) +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1, alpha = 0.8) +
    stat_summary(fun.data = mean_se, geom = "errorbar", fun.args = list(mult = 1.96),
                 width = 0.4, color = "black", size = 0.6) +
    scale_fill_manual(values = c('#66bd63','coral2','dodgerblue2')) + 
    ylab("Mean z") + scale_y_continuous(limits = c(-0.22,0.42), expand = c(0,0),
                                        breaks = seq(-0.4,0.4,by = 0.1)) +
    ggtitle("Retrieval Precision Dependence") + geom_hline(yintercept = 0) +
    scale_x_discrete(labels=c("Color.P\nScene.P","Color.S\nScene.P","Scene.S\nColor.P")) +
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 20), axis.title = element_text(size = 24),
          panel.background = element_blank(),
          legend.position="none", text = element_text(family="Helvetica"))   

plot(p1)
ggsave('Precision_Dependency.jpg', plot = p1, dpi = 300, width = 6, height = 5)

#t-tests, greater than 0?
pander(t.test(precision$Dependency[precision$Pair == 'ColorP-SceneP'], mu=0))
pander(t.test(precision$Dependency[precision$Pair == 'ColorS-SceneP'], mu=0))
pander(t.test(precision$Dependency[precision$Pair == 'SceneS-ColorP'], mu=0))

# for saving data in csv:
precision <- precision %>%
               spread(key = Pair, value = Dependency)
group_data <- merge.data.frame(group_data,precision,by='SubID') %>%
                sortFrame(SubID)

```

```{r}
write.csv(group_data, "Behavioral_data.csv", row.names=FALSE)
```