---
title: "Orbit fMRI - CONN glm ROI PPI Analyses"
output:
  html_notebook:
    code_folding: hide
    fontsize: 6pt
    theme: spacelab
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
---
<style type="text/css">
body{ /* Normal  */
      font-size: 14px}
td {  /* Table  */
  font-size: 12px}
h1.title {
  font-size: 30px}
h1 { /* Header 1 */
  font-size: 24px}
h2 { /* Header 2 */
    font-size: 20px}
code.r{ /* Code block */
    font-size: 12px}
</style>

* gPPI analyses are conducted in CONN by predicting each target time series with a seed ROI, psychological parametric modulators, convolved with the HRF, and the seed x psych interaction terms.  

* The connectivity change (interaction beta estimate) for each seed-target pair per subject and condition was then extracted and further analyzed at the group level here.  

* Connectivity beta estimates reflects the postive or negative change in connectivity estimates with *increasing* memory during 'remember' events.   

* Analyses use MNI-space unsmoothed data.  

```{r, include=FALSE}

library('ggplot2')
library('gridExtra')
library('grid')
library('cowplot')
library('ggpubr')
library('ggridges')
library('tidyr')
library('dplyr')
library('ez')
library('lsr')
library('psych')
library('reshape2')
library('knitr')
library('pander')

se <- function(x) sqrt(var(x)/length(x))  #function to calculate SE

### define computer path
#myComp <- '/Users/memolab/Google Drive/'
myComp <- '/Users/rosecooper/Documents/'

# where are my first level CONN matrices
matrixPath <- paste(myComp,'Work/Boston/ORBIT/analysis/fMRI/Orbit/FunctionalConnectivity/conn-roiData/',sep="")

### load in conn functions:
source(paste(myComp,'MemoLab/Manuscripts/SUBMITTED/Orbit-fMRI/paper-OrbitfMRI-repo/analysis/gPPI_functions_paper.R',sep=""))

space <- 'MNI-unsmoothed'

seeds        <- c("ANG","PREC","PCC","RSC","PHC","pHIPP","aHIPP","PRC","AMYG","FUS","ITC","OFC") #no 'L' or 'R' after means bilateral
ROIs         <- seeds
networks     <- c(1,1,1,1,1,2,2,3,3,3,3,3)  #network assignments to match to above seeds
networkNames <- c("PM","HIPP","AT")

sOrder   <- c(3,11,7,12,8,9,1,10,2,4,5,6) #to re-order to above seeds whe R default to order alphabetically
nOrder   <- c(3,2,1)

event <- 'Remember'
type  <- 'greater'

```

# Memory Quality
Change in connectivity between each target-seed pair with increasing memory detail (min 0, max 3 on any trial)  

## Overall and Hipp connectivity
```{r, fig.width=4,fig.height=4}

model <- 'Overall-Complexity-noEmot'
contrast <- "DetailRemembered"      # memory parametric modulator

# GET PPI MATRIX ------------------------------------------------------------------
### fmri subjects for this model:
subjects = list.dirs(path = paste(matrixPath,model,'_ROI-to-ROI/',sep = ""), full.names = FALSE, recursive = FALSE)

### get ppi matrix per subject for this contrast
ppiMatrix <- format_conn(matrixPath, seeds, subjects, model, contrast, event)
MemoryQualityPPI <- ppiMatrix

### get overall change in connectivity with memory:
meanConn <- data.frame(ConnectivityChange = apply(ppiMatrix, c(3), mean))
sum <- meanConn %>% summarise(Mean.Connectivity = mean(ConnectivityChange), SE.Connectivity = se(ConnectivityChange))
print(kable(sum))
# test against zero
pander(t.test(meanConn$ConnectivityChange, mu=0, alternative=type))


### focus on on aHIPP and pHIPP in terms of mean inter-network connectivity change with PM and AT networks (both as seeds and targets)
meanHipp <- mean_hipp_change(subjects, ppiMatrix, seeds, networks)
p <- plot_hipp(meanHipp)
plot(p)
ggsave('Remember_Hipp-to-Network.jpg',plot=last_plot(),dpi=300,width=5,height=5)
# Anova:
pander(ezANOVA(data = meanHipp, dv = MeanConnectivity, wid = Subject, 
        detailed = TRUE, within = .(Network,Region)))
# test against zero
pander(t.test(meanHipp$MeanConnectivity[meanHipp$Network == 'AT' & meanHipp$Region == 'aHIPP'], mu=0, alternative=type))
pander(t.test(meanHipp$MeanConnectivity[meanHipp$Network == 'PM' & meanHipp$Region == 'aHIPP'], mu=0, alternative=type))
pander(t.test(meanHipp$MeanConnectivity[meanHipp$Network == 'AT' & meanHipp$Region == 'pHIPP'], mu=0, alternative=type))
pander(t.test(meanHipp$MeanConnectivity[meanHipp$Network == 'PM' & meanHipp$Region == 'pHIPP'], mu=0, alternative=type))

write.csv(meanHipp, "Hipp-Network_MemoryQuality.csv", row.names=FALSE)

```

## Network connectivity
```{r, fig.width=5,fig.height=4}

# GET CONNECTIVITY CHANGE BY NETWORK ---------------------------------------------
networkMatrix <- ppi_Network_connectivity(subjects, ppiMatrix, networks)

### p-value for each network comparison:
netStats <- get_network_pValues(networkMatrix, networkNames, nOrder, type)
print(kable(netStats))

### plot:
p <- plot_Network(netStats, type)
plot(p)
ggsave('Remember_MemoryQuality_Network.jpg',plot=last_plot(),dpi=300,width=7.5,height=6)

```

## ROI-ROI connectivity
```{r, fig.width=5,fig.height=4}

### get p-values for each individual seed-target comparison
ppiStats <- get_ppi_stats(ppiMatrix, seeds, sOrder, type)

### plot mean PPI matrix
p <- plot_meanPPI(ppiStats, 1, 2.6)
plot(p)

# now print the individually significant connections:
print(kable(subset(ppiStats,sig == '*')))

```

# Color Precision
Calculates the change in connectivity between each target-seed pair with increasing color precision
## Overall connectivity
```{r, fig.width=4,fig.height=4}

model <- 'Features-SuccessPrecision-noEmot'
contrast <- "ColorPrecision"      # memory parametric modulator

# GET PPI MATRIX ------------------------------------------------------------------
### fmri subjects for this model:
subjects = list.dirs(path = paste(matrixPath,model,'_ROI-to-ROI/',sep = ""), full.names = FALSE, recursive = FALSE)

### get ppi matrix per subject for this contrast
ppiMatrix <- format_conn(matrixPath, seeds, subjects, model, contrast, event)
ColorPrecisionPPI <- ppiMatrix

### get overall change in connectivity with memory:
meanConn <- data.frame(ConnectivityChange = apply(ppiMatrix, c(3), mean))
sum <- meanConn %>% summarise(Mean.Connectivity = mean(ConnectivityChange), SE.Connectivity = se(ConnectivityChange))
print(kable(sum))
# test against zero
pander(t.test(meanConn$ConnectivityChange, mu=0, alternative=type))

```

## Network connectivity
```{r, fig.width=5,fig.height=4}

# GET CONNECTIVITY CHANGE BY NETWORK ---------------------------------------------
networkMatrix <- ppi_Network_connectivity(subjects, ppiMatrix, networks)

### p-value for each network comparison:
netStats <- get_network_pValues(networkMatrix, networkNames, nOrder, type)
print(kable(netStats))

### plot:
p <- plot_Network(netStats, type)
plot(p)
ggsave('Remember_ColorPrecision_Network.jpg',plot=last_plot(),dpi=300,width=7.5,height=6)

```

## ROI-ROI connectivity
```{r, fig.width=5,fig.height=4}

### get p-values for each individual seed-target comparison
ppiStats <- get_ppi_stats(ppiMatrix, seeds, sOrder, type)

# plot significant PRC/AMYG/PHC/RSC connections
p <- plot_seed_connections(ppiMatrix, ppiStats, 'Color', seeds)
plot(p)
ggsave('Remember_ColorPrecision_Connections.jpg',plot=last_plot(),dpi=300,width=6,height=4.5)

# now print the individually significant connections:
connections <- subset(ppiStats, pFDRSeed < .05 & (seeds == 'RSC' | seeds == 'PHC' | seeds == 'PRC' | seeds == 'AMYG'))
connections <- connections[,-c(5,6,8)]
print(kable(connections))

```

# Scene Precision
Calculates the change in connectivity between each target-seed pair with increasing scene precision
## Overall connectivity
```{r, fig.width=4,fig.height=4}

model <- 'Features-SuccessPrecision-noEmot'
contrast <- "ScenePrecision"      # memory parametric modulator

# GET PPI MATRIX ------------------------------------------------------------------
### fmri subjects for this model:
subjects = list.dirs(path = paste(matrixPath,model,'_ROI-to-ROI/',sep = ""), full.names = FALSE, recursive = FALSE)

### get ppi matrix per subject for this contrast
ppiMatrix <- format_conn(matrixPath, seeds, subjects, model, contrast, event)
ScenePrecisionPPI <- ppiMatrix

### get overall change in connectivity with memory:
meanConn <- data.frame(ConnectivityChange = apply(ppiMatrix, c(3), mean))
sum <- meanConn %>% summarise(Mean.Connectivity = mean(ConnectivityChange), SE.Connectivity = se(ConnectivityChange))
print(kable(sum))
# test against zero
pander(t.test(meanConn$ConnectivityChange, mu=0, alternative=type))

```

## Network connectivity
```{r, fig.width=5,fig.height=4}

# GET CONNECTIVITY CHANGE BY NETWORK ---------------------------------------------
networkMatrix <- ppi_Network_connectivity(subjects, ppiMatrix, networks)

### p-value for each network comparison:
netStats <- get_network_pValues(networkMatrix, networkNames, nOrder, type)
print(kable(netStats))

### plot:
p <- plot_Network(netStats, type)
plot(p)
ggsave('Remember_ScenePrecision_Network.jpg',plot=last_plot(),dpi=300,width=7.5,height=6)

```

## ROI-ROI connectivity
```{r, fig.width=5,fig.height=4}

### get p-values for each individual seed-target comparison
ppiStats <- get_ppi_stats(ppiMatrix, seeds, sOrder, type)

# plot significant PRC/AMYG/PHC/RSC connections
p <- plot_seed_connections(ppiMatrix, ppiStats, 'Scene', seeds)
plot(p)
ggsave('Remember_ScenePrecision_Connections.jpg',plot=last_plot(),dpi=300,width=7,height=4.5)

# now print the individually significant connections:
connections <- subset(ppiStats, pFDRSeed < .05 & (seeds == 'RSC' | seeds == 'PHC' | seeds == 'PRC' | seeds == 'AMYG'))
connections <- connections[,-c(5,6,8)]
print(kable(connections))

```

# Color vs Scene Connections
a) Similarity - pearson's correlation - between the connectivity change patterns associated with item color and spatial precision  
b) PM seed (PHC & RSC) vs AT seed (PRC & AMYG) to ANG/PREC by feature  
```{r, fig.width=5,fig.height=5}

# a) calculate the overall pattern simiarity between the color precision and scene precision ROIxROI matrices within each subject
similarity <- feature_similarity(ColorPrecisionPPI, ScenePrecisionPPI)
sum <- similarity %>% summarise(Mean.Z = mean(Similarity), SE.Z = se(Similarity))
print(kable(sum))
# test against zero
pander(t.test(similarity$Similarity, mu=0, alternative=type))

# b) compare PM and AT seeds to common ANG/PREC targets by feature
features <- feature_connections(ColorPrecisionPPI, ScenePrecisionPPI, seeds, subjects)
feature_data <- features[[1]]
sum <- feature_data %>% group_by(SeedNetwork, Feature) %>%
                     summarise(Conn = mean(Connectivity), SE.Conn = se(Connectivity))
print(kable(sum))

# Anova:
pander(ezANOVA(data = feature_data, dv = Connectivity, wid = SubID,
        detailed = TRUE, within = .(SeedNetwork,Feature)))

# t-test for PM (color vs scene):
pander(t.test(Connectivity ~ Feature, data=feature_data[feature_data$SeedNetwork == 'PM',], paired=TRUE))
# t-test for AT (color vs scene):
pander(t.test(Connectivity ~ Feature, data=feature_data[feature_data$SeedNetwork == 'AT',], paired=TRUE))

plot(features[[2]])
ggsave('Remember_Network-to-ANGPREC.jpg',plot=last_plot(),dpi=300,width=6,height=7)

write.csv(feature_data, "Feature_Connections.csv", row.names=FALSE)

```

```{r}
### save data
save(ROIs, MemoryQualityPPI, ColorPrecisionPPI, ScenePrecisionPPI, file = "Memory_gPPI_data.RData")
```
