---
title: "Orbit fMRI - ROI Background Connectivity Analyses"
output:
  html_notebook:
    code_folding: hide
    fontsize: 6pt
    theme: spacelab
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
---
<style type="text/css">
body{ /* Normal  */
      font-size: 14px}
td {  /* Table  */
  font-size: 12px}
h1.title {
  font-size: 30px}
h1 { /* Header 1 */
  font-size: 24px}
h2 { /* Header 2 */
    font-size: 20px}
code.r{ /* Code block */
    font-size: 12px}
</style>

* Task background connectivity are run in CONN using a similar procedure to memory-modulated gppi analyses. However, instead of including task-related covariates as parametric modulators, here task-related covariates are regresssed out, along with FD, aCompCor, and motion, at the first-level de-noising step. 

* Analyses use MNI-space unsmoothed data.  

* Connectivity measures this reflect the 'background' or task-independent connections between bilateral ROIs, during either encoding or remember events. Thresholded at r > 0.25.

```{r, include=FALSE}

library('ggplot2')
library('gridExtra')
library('grid')
library('cowplot')
library('ggpubr')
library('ggridges')
library('tidyr')
library('dplyr')
library('ez')
library('lsr')
library('psych')
library('reshape2')
library('NetworkToolbox')
library('knitr')
library('pander')

se <- function(x) sqrt(var(x)/length(x))  #function to calculate SE

### define computer path
#myComp <- '/Users/memolab/Google Drive/'
myComp <- '/Users/rosecooper/Documents/'

# where are my first level CONN matrices
matrixPath <- paste(myComp,'Work/Boston/ORBIT/analysis/fMRI/Orbit/FunctionalConnectivity/conn-roiData/',sep="")

### load in conn functions:
source(paste(myComp,'MemoLab/Manuscripts/Orbit-fMRI/paper-OrbitfMRI-repo/analysis/background_functions_paper.R',sep=""))

seeds        <- c("ANG","PREC","PCC","RSC","PHC","pHIPP","aHIPP","PRC","AMYG","FUS","ITC","OFC")
networks     <- c(1,1,1,1,1,2,2,3,3,3,3,3)  #network assignments to match to above seeds
networkNames <- c("PM","HIPP","AT")

sOrder   <- c(3,11,7,12,8,9,1,10,2,4,5,6) #to re-order to above seeds whe R default to order alphabetically
nOrder   <- c(3,2,1)

```

# ROI-to-ROI connections
## Encoding
```{r, fig.width=5,fig.height=5}

##### Threshold for matrices:
th <- 0.25

model <- 'Task-Connectivity_weighted_ROI-to-ROI'
### fmri subjects:
subjects = list.dirs(path = paste(matrixPath,model,'/',sep = ""), full.names = FALSE, recursive = FALSE)


##### ROI x ROI for Encoding #######
event <- 'Encoding'
title <- event

# GET ROI-ROI connections  ------------------------------------------------------------------
connMatrixE <- format_conn(matrixPath, seeds, subjects, model, event)

### get p-values for each seed-target comparison --> connectivity significant?
type = 'greater'
connPValues <- get_conn_pValues(connMatrixE, seeds, sOrder, type, th)

### plot mean conn matrix
p <- plot_meanconn(connMatrixE, connPValues, seeds, sOrder, title, type, th)
plot(p)
ggsave(paste('Encoding_Background_ROI-ROI_',th,'.jpg',sep=""),plot=last_plot(),dpi=300,width=8,height=9.5)

```

## Remember
```{r, fig.width=5,fig.height=5}

##### ROI x ROI for Retrieval #######
event <- 'Retrieval'
title <- event

# GET ROI-ROI connections  ------------------------------------------------------------------
connMatrixR <- format_conn(matrixPath, seeds, subjects, model, event)

### get p-values for each seed-target comparison --> connectivity significant?
type = 'greater'
connPValues <- get_conn_pValues(connMatrixR, seeds, sOrder, type, th)

### plot mean conn matrix
p <- plot_meanconn(connMatrixR, connPValues, seeds, sOrder, title, type, th)
plot(p)
ggsave(paste('Retrieval_Background_ROI-ROI_',th,'.jpg',sep=""),plot=last_plot(),dpi=300,width=8,height=9.5)

```

## Remember-Encoding
```{r, fig.width=5,fig.height=5}

##### ROI x ROI for Difference #######
event <- 'Remember-Encoding'
title <- event

# GET ROI-ROI connections  ------------------------------------------------------------------
connMatrix <- connMatrixR - connMatrixE

### get p-values for each seed-target comparison --> connectivity significant?
type = 'two.sided'
connPValues <- get_conn_pValues(connMatrix, seeds, sOrder, type, th)

### plot mean conn matrix
p <- plot_meanconn(connMatrix, connPValues, seeds, sOrder, title, type, th)
plot(p)
ggsave(paste('Retrieval-Encoding_Background_ROI-ROI_',th,'.jpg',sep=""),plot=last_plot(),dpi=300,width=8,height=9.5)

```

# Modularity
```{r, fig.width=3,fig.height=4}

# Get modularity by subject onn thresholded, weighted matrix:
# Encoding and Retrieval:
mod <- run_modularity(connMatrixE, connMatrixR, subjects, th)
mod$Task <- as.factor(mod$Task)
mod$Subject <- as.factor(mod$Subject)

# plot
p <- ggplot(mod, aes(x = Task, y=Modularity, fill=Task)) +
    stat_summary(fun.y = mean, geom="bar", alpha = 0.6, color = 'gray10', position = position_dodge(1)) +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1, alpha = 0.8, position = position_dodge(1)) +
    stat_summary(fun.data = mean_se, geom = "errorbar", fun.args = list(mult = 1.96),
                 width = 0.45, color = "black", size = 0.65, position = position_dodge(1)) +
    scale_fill_manual(values = c('gray50','gray80')) + geom_hline(yintercept = 0) + ylab("Mean Q") +
    ggtitle("Modularity") +
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 22), axis.title = element_text(size = 24), panel.background = element_blank(),
          legend.position="none", text = element_text(family="Helvetica")) 
plot(p)
ggsave(paste('Modularity_',th,'.jpg',sep=""), plot = last_plot(), dpi = 300, width = 4.2, height = 5)

# t-test on change in modularity:
mod <- data.frame(mod)
pander(t.test(Modularity ~ Task, data=mod, paired=TRUE))

```

# Between vs Within Network Connectivity
```{r, fig.width=5,fig.height=4}

# Get modularity by subject onn thresholded, weighted matrix:
# Encoding and Retrieval:
network <- run_network(connMatrixE, connMatrixR, subjects, networks, th)
network$Measure <- as.factor(network$Measure)
network$Task <- as.factor(network$Task)
network$Subject <- as.factor(network$Subject)

# plots retrieval vs encoding within vs between network connectivity:
p <- ggplot(network, aes(x = Measure, y=Strength, fill=Task)) +
    stat_summary(fun.y = mean, geom="bar", alpha = 0.6, color = 'gray10', position = position_dodge(1)) +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1, alpha = 0.8, position = position_dodge(1)) +
    stat_summary(fun.data = mean_se, geom = "errorbar", fun.args = list(mult = 1.96),
                 width = 0.45, color = "black", size = 0.65, position = position_dodge(1)) +
    scale_fill_manual(values = c('gray50','gray80')) + geom_hline(yintercept = 0) + ylab("Mean Stength") + 
    ggtitle("Network Density") +
    theme(plot.title = element_text(hjust = 0.5, size=28), axis.line = element_line(colour = "black"), 
          axis.text = element_text(size = 22), axis.title = element_text(size = 24), panel.background = element_blank(),
          text = element_text(family="Helvetica")) 
plot(p) 
ggsave(paste('NetworkStrength_',th,'.jpg',sep=""), plot = last_plot(), dpi = 300, width = 6, height = 5)

#RUN ANOVA
pander(ezANOVA(data = network, dv = Strength, wid = Subject, 
        detailed = TRUE, within = .(Measure,Task)))

# within > between for both tasks (is PMAT structure valid?)
encoding <- subset(network, Task == 'Encoding')
pander(t.test(Strength ~ Measure, data=encoding, paired=TRUE))

retrieval <- subset(network, Task == 'Retrieval')
pander(t.test(Strength ~ Measure, data=retrieval, paired=TRUE))

```

```{r}
### save data
backgroundEncoding  <- connMatrixE # fisher z subject-specific connectivity matrices
backgroundRetrieval <- connMatrixR # ""
modularity <- mod
density <- network
ROIs <- seeds

save(ROIs, backgroundEncoding, backgroundRetrieval, modularity, density, file = "Background_connectivity_data.RData")
```